On The Impact of Atoms of Confusion in JavaScript Code

### 2022-07-02 method_replication_study.tex
Added data for the replication study, specifically about the number of errors and correct guesses for obfuscated and clear versions and also about time require for correct and incorrect responses.

The second section presents the programs, one at a time. For each one, there is a text box where the answer should be written. There is also an ``I do not know'' button, which, when clicked, leads the subject to the next question. In our setting, ``I do not know'' was treated as a wrong answer. To reduce the likelihood of a subject leveraging attempting to execute the programs, the web application verifies whether the subject attempts to change tabs or windows and presents the programs as images, instead of text. Upon submitting an answer for a particular program, the subject is automatically led to a similar page, containing the next one.

>>>>

The second section presents the programs, one at a time. For each one, there is a text box where the answer should be written. There is also an ``I do not know'' button, which, when clicked, leads the subject to the next question. In our setting, ``I do not know'' is treated as a wrong answer. To reduce the likelihood of a subject attempting to execute the programs, the web application verifies whether the subject attempts to change tabs or windows and presents the programs as images, instead of text. Upon submitting an answer for a particular program, the subject is automatically led to a similar page, containing the next one.
